A parametric system for contour parallel variable width toolpath generation

### 2019-08-08 4_method.tex
fix transition length viability constraint

A transition with length $t(n)$ will be placed somewhere covering the anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.

@@

\iffalse
\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{
Transition placement.
The anchor position within the transition length is proportional to the transition location within the range between two distances with preferred length. 
}
\label{transition_placement}
\end{figure}
\fi

@@

The following restrictions hold:
\begin{itemize}
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\item $t$ is viable:  \todo{TODO: verify this.} \\ $t_1(n) + t_0(n+1) < \left( b^{-1}(n + 1) - b^{-1}(n) \right) /{2 \cos \alpha_\text{max}}$
\end{itemize}

>>>>

A transition with length $t(n)$ will be placed somewhere covering the anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
The transitions lengths should be such that they fit between anchor locations of two consecutive transitions even for a bone with high bisector angle:
$$t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$$
for each $n \in \mathbb{N}$.
See \cref{transition_placement}.

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
\caption{
Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a skeleton segment (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
}
\label{transition_placement}
\end{figure}

@@

@@

The following restrictions hold:
\begin{itemize}
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}
